IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/retrofit.tex
yo

\paragraph{Exceptions}  One language feature that has caused difficulty for
many information flow control systems is handling exceptions.
%
The key difficulty appears when considering the propagation of exceptions
across stack boundaries where the current label is restored, e.g., from secret
to public, as done by LIO's |toLabeled| and Breeze's
brackets~\cite{Hritcu:2013:YIB:2497621.2498098, stefan:2012:arxiv-flexible}.
%
If the exception crosses this boundary, it can leak information about the
inner secret computation into a public computation.

At first glance, it does not appear that our system has any such operator;
there are only tasks, and the correct behavior for a task throwing
an exception is self-evident: it should simply be removed from the scheduler.
However, under a \emph{sequential scheduler} (such as |seqf|),
the behavior of |sandbox|
can be used to model the behavior of such an operator:
\begin{align*}
    & |toLabeled l te @= | \\
    & |tab let i = taskId; | \\
    & |tab let j = TI (sandbox (IT (TI (setLabel l); TI (send i l (IT te)))))| \\
    & |tab in (\ _ . TI (setLabel l); TI (recvf x _ x unit))|
\end{align*}
When the sequential scheduler is used, the sandboxed task runs to
completion before returning to the task that sandboxed it.  Thus,
a task list should rather be interpreted as a number of information flow
aware stack frames.  To read the result of a |toLabeled| operation
(which is communicated via message passing), the parent task must raise
its label; otherwise the label will get dropped, as per the \textsc{I-recv} rule.\footnote{A keen reader may note that with a single, per-task
channel, we might mix up our messages.  Indeed, a proper development requires
the ability to allocate fresh channels; for purposes of simplicity, this
has been omitted.}

In this setting, it is also clear that exceptions should not cross boundaries,
as seen in |toLabeled l fail; true|, which evaluates to |true| no matter even in
the event of an exception inside of the |toLabeled| block:
\todo{sh}{leaving this to ds, who wanted to finish the example}

>>>>

\paragraph{Exceptions}  One language feature that has caused difficulty for
many information flow control systems is handling exceptions.
%
The key difficulty appears when considering the propagation of exceptions
across stack boundaries where the current label is restored, e.g., from secret
to public, as done by LIO's |toLabeled| and Breeze's
brackets~\cite{Hritcu:2013:YIB:2497621.2498098, stefan:2012:arxiv-flexible}.
%
If the exception crosses this boundary, it can leak information about the
inner secret computation into a public computation; hence, both systems
explicitly ensure that |toLabeled| does not propagate exceptions.

Our general embedding approach provides these semantics by construction.
%
To show this, consider, first, the encoding of the sequential |toLabeled|
construct in our framework:
\begin{align*}
    & |toLabeled l te @= | \\
    & |tab let i = taskId; | \\
    & |tab let j = TI (sandbox (IT (TI (setLabel l); TI (send i l (IT te)))))| \\
    & |tab in (\ _ . TI (setLabel l); TI (recvf x _ x unit))|
\end{align*}
When using the sequential scheduler |seqf|, the sandboxed task runs to
completion before returning to the task that sandboxed it. 
(Here, a task list can be interpreted as a number of information flow aware
stack frames.)
To read the result of a |toLabeled| operation
(which is communicated via message passing), the parent task must raise
its label; otherwise the label will get dropped, as per the \textsc{I-recv}
rule.\footnote{A keen reader may note that with a single, per-task channel, we
might mix up our messages.  Indeed, a proper development requires the ability
to allocate fresh channels; for purposes of simplicity, this has been omitted.}

Second, suppose that our |targetLangML| is extended with a single exception
expression |fail|, which reduces to |fail|, removing all containing |tE|
evaluation contexts, i.e., it propagates up to a |IT (-)| boundary.
%
In this setting, it is clear that exceptions cannot cross boundaries.
%
For instance, 
\begin{code}
TI(toLabeled l (IT (if te then fail else true))); true
\end{code}
always evaluates to |true|, regardless of the value of |te|.
%
As in both LIO and Breeze, however, only when calling |recv| on such messages
will the exception be propagated.
%
This of course, is not a leak since the current label must be raised before
receiving sensitive message, regardless of their content.
